---
title: "Fertility Project"
author: "Luis Fernando Garc&iacute;a Acosta and Carlos Daniel Ruvalcaba Serrano"
date: October 10, 2018
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Introduction
Using R a data analysis programming language and KNN K nearest neighbors is a simple algorithm that stores all available cases and classifies new cases based on a similarity measure, we are going to analyze a dataset where 100 volunteers provide a semen sample analyzed according to the WHO 2010 criteria. Sperm concentration are related to socio-demographic data, environmental factors, health status, and life habits. The main goal is to predict whether a patient´s
sperm quality it's ALTERED or NORMAL.<br/>
Despite of we are going to deal with data classification, KNN application and final result interpretation.


We hope you enjoy it!

-Luis Fernando García, Carlos Daniel Ruvalcaba Serrano
 Autonomus University of Zacatecas, Mexico.

# Exploring the Dataset.
```{r,echo=FALSE}
```


## Exploring the Dataset.
The first thing to notice it's that we have 100 instances
```{r, echo=TRUE}
ferti_data <- read.table("fertility_Diagnosis.txt",header=TRUE,sep = ",")
nrow(ferti_data)
```
The second thing to noticce it's that we have 10 attributes
```{r,echo=TRUE}
ncol(ferti_data)
```
## Exploring the dataset
<strong>Each instance contains the next characteristics </strong>
  <br/><br/>-Season: Season in which the analysis was performed<br/><br/>
  -Age: Age of the patient<br/><br/>
  -Child_Disease: If the patient had some children disease (ie , chicken pox, measles, mumps, polio)<br/><br/>
  -Accident: If the patient had an accident or a serious trauma<br/><br/>
  -Surge: Patient had surgical intervention<br/><br/>
  -Fever: High fevers in the last year<br/><br/>
  -AlcoholConsumption: Frequency of alcohol consumption<br/><br/>

## Exploring the dataset
  -Smoke: If the patient smokes<br/><br/>
  -Hours Sitting: Number of hours spent sitting per day <br/><br/>
  -Diagnosis: Patients sperm quality<br/><br/>
  
##Exploring the Dataset.
<strong>Season</strong>
Season describes in which season of the year the study was made.<br/><br/>
 -Winter: -1 <br/><br/>
 -Spring: -0.33<br/><br/>
 -Summer: .33<br/><br/>
 -Fall: 1<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Season)

```

##Exploring the Dataset.
<strong>Age</strong>
Age describes the age of the patient at the time of analysis. The age goes from 18 to 36<br/><br/>
  -Age 0 to 1<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Age)

```

##Exploring the Dataset.
<strong>Child_Disease</strong>
Child_disease describes if the pateint sufferd a Childish diseases<br/><br/>
  -Yes: 0 <br/><br/>
  -No: 1<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Child_Disease)

```


##Exploring the Dataset.
<strong>Accident</strong>
Accident describes if a patient had an accident or serious trauma
<br/><br/>
  -Yes: 0 <br/><br/>
  -No: 1<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Accident)

```


##Exploring the Dataset.
<strong>Surge</strong>
Surge describes if the patient has been Surgical intervention 
<br/><br/>
  -Yes: 0 <br/><br/>
  -No: 1<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Accident)

```

##Exploring the Dataset.
<strong>Fever</strong>
<br/><br/>Fever describes if the patient has had a high fevers in the last year 
<br/><br/>
  -Less than three months ago: -1 <br/><br/>
  -More than three months ago: 0<br/><br/>
  -No: 1<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Fever)

```
##Exploring the Dataset.
<strong>AlcoholConsumption</strong>
<br/><br/> AlcoholConsumption describes frequency of alcohol consumption of a patient
<br/><br/>
  -1 : several times a day <br/><br/>
  -2 :  every day <br/><br/>
  -3 : several times a week <br/><br/>
  -4 :  once a week <br/><br/>
  -5 :  hardly ever or never <br/><br/>

##Exploring the Dataset.
AlcoholConsumption goes from 0 to 1<br/>
```{r,echo=TRUE}
  summary(ferti_data$AlcoholConsumption)
```

##Exploring the Dataset.
<strong>Smoke</strong>
<br/><br/> Smoke describes the patient's smoking habit
<br/><br/>
  -1 : never <br/><br/>
   0 : occasional<br/><br/>
   1 : daily <br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Smoke)
```
  
##Exploring the Dataset.
<strong>Hours Sitting</strong>
<br/><br/> Hours Sitting describes the number of hours spent sitting per day
<br/><br/>
  -1 : never <br/><br/>
   0 : occasional<br/><br/>
   1 : daily <br/><br/>
  The hours goes from 0 to 12<br/>
```{r,echo=TRUE}
  summary(ferti_data$Hours.Sitting)
```
##Exploring the Dataset.
<strong>Diagnosis</strong>
<br/><br/> The final diagnosis if the patients sperm quality is normal or altered
<br/><br/>
   N : Normal <br/><br/>
   A : Altered<br/><br/>
```{r,echo=TRUE}
  summary(ferti_data$Diagnosis)
```


## Slide with R Output


```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

